Quality measure notes

### 2021-07-24 StateOfPractice/Ao-Report/13Methods.tex
MI report - updated ch 4

We designed the following nine sections in the template for the nine software qualities mentioned in Section \ref{sec_software_quality}. For each quality, we ask several questions and the typical answers are among the collection of ``yes'', ``no'', ``n/a'', ``unclear'', a number, a string, a date, a set of strings, etc. Each quality needs an overall score between 1 and 10 based on all the previous questions. For some qualities, the empirical measurements also affect the score.

All the last three sections are about the empirical measurements. We use two command-line software tools \textit{GitStats} and \textit{scc} to extract information from the source code repositories. For projects held on GitHub, we manually collect additional metrics, such as the stars of the GitHub repository, and the numbers of open and closed pull requests. Section \ref{sec_empirical_measurements} presents more details about the empirical measurements.

>>>>

We designed the following nine sections in the template for the nine software qualities mentioned in Section \ref{sec_software_quality}. For each quality, we ask several questions and the typical answers are among the collection of ``yes'', ``no'', ``n/a'', ``unclear'', a number, a string, a date, a set of strings, etc. Each quality needs an overall score between 1 and 10 based on all the previous questions. For some qualities, we perform surface measurements, which allow us to carry out on all packages with reasonable efforts. The surface measurements reveal some traits of a underlying quality, but may not fully represent it.

\begin{itemize}
\item \textbf{Installability} We check the existence and quality of installation instructions. The user experience is also an important factor, such as the ease to follow the instructions, number of steps, automation tools, and the prerequisite steps for the installation. If any problem interrupts the process of installation or uninstallation, we give a lower score to this quality. We also record the operating system for the installation test and whether we can verify the installation.

\item \textbf{Correctness \& Verifiability} For \textit{correctness}, we check the projects to identify the techniques to ensure this quality, such as literate programming, automated testing, symbolic execution, model checking, unit tests, etc. We also examine whether the projects use continuous integration. For \textit{verifiability}, we go through the documents of the projects to check the requirements specifications, theory manuals, and getting started tutorials. If a getting started tutorial exists and provides expected results, we follow it and check if the outputs match.

\item \textbf{Surface Reliability} We check that whether the software break during the installations and tutorials, whether there are descriptive error messages, and if we can recover the process after the errors.

\item \textbf{Surface Robustness} We check that how the software handle unexpected/unanticipated input. For example, for software packages with the function to load image files, we prepare broken image files for them to open. We use a text file (.txt) with a modified extension name (.dcm) as an unexpected/unanticipated input. We load a few correct input files to ensure the function is working correctly before testing with the unexpected/unanticipated ones.

\item \textbf{Surface Usability} We examine the documents of the projects and consider software with a getting started tutorial and a user manual easier to use. Meanwhile, we check if users have any channels to get supports. Our impressions and user experiences when testing the software also affect the scores. For example, easy-to-use graphical user interfaces give us a better experience, thus lead to better scores.

\item \textbf{Maintainability} We search the projects' documents and identify the process of contributing and reviewing code. We believe that the artifacts of a project - including source code, documents, building scripts, etc. - can significantly affect its  \textit{maintainability}. Thus we check each project for its artifacts, such as API documentation, bug tracker, release notes, test cases, build files, version control, etc. We also check the tools supporting issue tracking and version control and the percentages of closed issues and comment lines in code.

\item \textbf{reusability} We count the total number of code files for each project. Projects with a large number of components provide more choices to reuse. Furthermore, well modularized code, which tend to have smaller parts in separated files, are easier to reuse. Thus, we consider the projects with more code files to be more reusable. We use \textit{GitStats} as a tool to count the number of text-based files for all projects, and consider the projects with more text-based files to also have more code files. We also decide that the projects with API documentation can deliver better \textit{Reusability}.

\item \textbf{Surface Understandability} We randomly examine 10 code files. We check the code’s style within each code file, such as whether the identifiers, parameters, indentation, and formatting are consistent, whether the constants (other than 0 and 1) are hardcoded into the code, and whether the developers modularized the code. We also check the descriptive information for the code, such as documents mentioning the coding standard, the comments in the code, and the descriptions or links for algorithms in the code.

\item \textbf{Visibility/Transparency} To measure this quality, such as all of the steps of a software development process and the current status of a project, we check the existing documents. We examine the development process, current status, development environment, and release notes for each project. If any information is missing or poorly conveyed, the \textit{visibility/transparency} is not ideal.
\end{itemize}

All the last three sections are about the empirical measurements. For some qualities, the empirical measurements also affect the score. We use two command-line software tools \textit{GitStats} and \textit{scc} to extract information from the source code repositories. For projects held on GitHub, we manually collect additional metrics, such as the stars of the GitHub repository, and the numbers of open and closed pull requests. Section \ref{sec_empirical_measurements} presents more details about the empirical measurements.

### 2021-07-24 StateOfPractice/Ao-Report/14MeasurementResults.tex
MI report - updated ch 4

For some qualities, it might be a good idea to cross-compare with the empirical scores.

\section{Selected Software List}

\section{Installability}

\section{Correctness \& Verifiability}

\section{Reliability}

\section{Robustness}

\section{Usability}

\section{Maintainability}

\section{Reusability}

\section{Understandability}

\section{Visibility \& Transparency}

>>>>

This section shows the summary of the measurement results. The detailed data can be found in the repository \hyperlink{https://github.com/smiths/AIMSS}{https://github.com/smiths/AIMSS}.

Table \ref{tab_final_list} shows the 29 software packages that we measured. We tried to find the initial release dates in the documents, such as the introduction and release notes. We used the date of the latest change to each code repository to decide the latest update. We found out funding information for eight projects, and we are not sure about the rest.

We considered anyone who made at least one accepted commit to the source code as a contributor. Thus, it does not mean that any development teams had long-term members as many as 100. Many of these projects received change requests and code from the community, such as pull requests and git commits on GitHub.

Table \ref{tab_final_list} also shows the supported operating systems for each software package, and 25 of them could work on all three Windows (W), macOS (M), and Linux (L) systems. However, there was a significant difference in the philosophy to achieve cross-platform compatibility. Most of them were native software products, but five were naturally platform-independent web applications.

\begin{table}[H]
\begin{tabular}{lllllllll}
\hline
\multirow{2}{*}{Software} & \multirow{2}{*}{Released} & \multirow{2}{*}{Updated} & \multirow{2}{*}{Contributors} & \multirow{2}{*}{Funded} & \multicolumn{3}{c}{OS} & \multirow{2}{*}{Web} \\ \cline{6-8}
 &  &  &  &  & W & M & L &  \\ \hline
3D Slicer \cite{Kikinis2014} & 1998 & 2020-08 & 100 & X & X & X & X &  \\
Ginkgo CADx \cite{Wollny2020} & 2010 & 2019-05 & 3 &  & X & X & X &  \\
XMedCon \cite{Nolf2003} & 2000 & 2020-08 & 2 &  & X & X & X &  \\
Weasis \cite{Roduit2021} & 2010 & 2020-08 & 8 &  & X & X & X &  \\
MRIcroGL \cite{Rorden2021} & 2015 & 2020-08 & 2 &  & X & X & X &  \\
SMILI \cite{Chandra2018} & 2014 & 2020-06 & 9 &  & X & X & X &  \\
ImageJ \cite{Rueden2017} & 1997 & 2020-08 & 18 & X & X & X & X &  \\
Fiji \cite{Schindelin2012} & 2011 & 2020-08 & 55 & X & X & X & X &  \\
DicomBrowser \cite{Archie2012} & 2012 & 2020-08 & 3 &  & X & X & X &  \\
3DimViewer \cite{TESCAN2020} & unclear & 2020-03 & 3 & X & X & X &  &  \\
Horos \cite{horosproject2020} & unclear & 2020-04 & 21 &  &  & X &  &  \\
OsiriX Lite \cite{PixmeoSARL2019} & 2004 & 2019-11 & 9 &  &  & X &  &  \\
dwv \cite{Martelli2021} & 2012 & 2020-09 & 22 &  & X & X & X & X \\
Drishti \cite{Limaye2012} & 2012 & 2020-08 & 1 &  & X & X & X &  \\
\begin{tabular}[c]{@{}l@{}}BioImage Suite\\ Web \cite{Papademetris2005}\end{tabular} & 2018 & 2020-10 & 13 & X & X & X & X & X \\
OHIF Viewer \cite{Ziegler2020} & 2015 & 2020-10 & 76 &  & X & X & X & X \\
Slice:Drop \cite{Haehn2013} & 2012 & 2020-04 & 3 &  & X & X & X & X \\
GATE \cite{Jan2004} & 2011 & 2020-10 & 45 &  &  & X & X &  \\
ITK-SNAP \cite{Yushkevich2006} & 2006 & 2020-06 & 13 & X & X & X & X &  \\
ParaView \cite{Ahrens2005} & 2002 & 2020-10 & 100 & X & X & X & X & X \\
MatrixUser \cite{Liu2016} & 2013 & 2018-07 & 1 &  & X & X & X &  \\
DICOM Viewer \cite{Afsar2021} & 2018 & 2020-04 & 5 & X & X & X & X &  \\
INVESALIUS 3 \cite{Amorim2015} & 2009 & 2020-09 & 10 &  & X & X & X &  \\
\end{tabular}
\end{table}

\begin{table}[H]
\begin{tabular}{lllllllll}
\hline
\multirow{2}{*}{Software} & \multirow{2}{*}{Released} & \multirow{2}{*}{Updated} & \multirow{2}{*}{Contributors} & \multirow{2}{*}{Funded} & \multicolumn{3}{c}{OS} & \multirow{2}{*}{Web} \\ \cline{6-8}
 &  &  &  &  & W & M & L &  \\ \hline
medInria \cite{Fillard2012} & 2009 & 2020-11 & 21 &  & X & X & X &  \\
dicompyler \cite{Panchal2010} & 2009 & 2020-01 & 2 &  & X & X &  &  \\
MicroView \cite{ParallaxInnovations2020} & 2015 & 2020-08 & 2 &  & X & X & X &  \\
Papaya \cite{UTHSCSA2019} & 2012 & 2019-05 & 9 &  & X & X & X &  \\
AMIDE \cite{Loening2017} & 2006 & 2017-01 & 4 &  & X & X & X &  \\
Gwyddion \cite{Nevcas2012} & 2004 & 2020-11 & 38 &  & X & X & X &  \\ \hline
\end{tabular}
\caption{\label{tab_final_list}Final software list}
\end{table}

Most of the projects used more than one programming language, including a primary language that the developers used the most. Figure \ref{fig_language} shows the primary languages versus the number of projects using them.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\centering
\begin{axis}
[
ybar,
height=8cm,
width=12cm,
ylabel={Number of projects},
xlabel={\ Primary language},
symbolic x coords={C++, JavaScript, Java, C, Python, Pascal, Matlab},
xtick=data,
nodes near coords,
nodes near coords align={vertical},
]
\addplot[black,fill=blue!55!black] coordinates {(C++,11) (JavaScript,6) (Java,4) (C,3) (Python,3) (Pascal,1) (Matlab,1) };
\end{axis}  
\end{tikzpicture}
\caption{\label{fig_language}Primary languages versus number of projects using them}
\end{figure}

We failed installing \textit{DICOM Viewer}, so we could not test \textit{surface reliability} and \textit{surface robustness} for it. We might underestimate the scores of the two qualities for this software. We kept this software on our list because the other seven qualities do not rely on a successful installation. Besides, it used a unique dependency, and we wanted to keep the diversity.

\section{Installability}
\label{sec_result_installability}

Figure \ref{fg_installability_scores} lists the scores of \textit{installability}.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/installability_scores.png}
\caption{AHP installability scores}
\label{fg_installability_scores}
\end{figure}

We found installation instructions for 16 projects. Among the ones without such an instruction, \textit{BioImage Suite Web} and \textit{Slice:Drop} were web applications and provided online versions to use, thus they needed no installation. Installing 10 of the projects needed extra dependencies. Five of them are the web applications in Table \ref{tab_final_list}, and depended on a browser; \textit{dwv}, \textit{OHIF Viewer}, and \textit{GATE} needed extra dependencies to build; \textit{ImageJ} and	\textit{Fiji} needed an unzip tool; \textit{MatrixUser} was based on Matlab; \textit{DICOM Viewer} needed to work on Nextcloud platform.

\textit{3D Slicer} has the highest score because it had easy-to-follow installation instructions, and the installation processes were automated, fast, and frustration-free, with all dependencies automatically added. There were also no errors during the installation and uninstallation steps. Many other software packages also had installation instructions and automated installers, and we had no trouble installing them, such as \textit{INVESALIUS 3}, \textit{Gwyddion}, \textit{XMedCon}, and \textit{MicroView}. We gave them various scores based on the understandability of the instructions, installation steps, and user experience. Since \textit{BioImage Suite Web} and \textit{Slice:Drop} needed no installation, we gave them higher scores due to the significant convenience. \textit{BioImage Suite Web} also provided an option to download cache to local for offline usage, which was easy to apply.

\textit{dwv}, \textit{GATE}, and \textit{DICOM Viewer} showed severe problems. We could not install them due to some issues that we could not solve. We spent a reasonable amount of time on these problems, then considered them major obstacles for normal users if we still did not figure out any solutions. We suspect that only a part of the users faced the same problems, and given a lot of time, we might be able to find solutions. However, the difficulties greatly impacted the installation experiences, and we graded these software packages with lower scores. For example, \textit{dwv} and \textit{GATE} had the option to build from the source code, and we failed the building processes following the instructions. Although we could not locally build them, we could use a deployed online version for \textit{dwv}, and a VM version for \textit{GATE}. With those, we finished all the measurements for them. Furthermore, \textit{DICOM Viewer} depended on a cloud platform, and we could not successfully install the dependency.

\textit{MatrixUser} has a lower score because it depended on Matlab. We considered installing Matlab takes many more steps and time, and some users may not have a license to use Matlab.

\section{Correctness \& Verifiability}
The scores of \textit{correctness \& verifiability} are shown in Figure \ref{fg_correctness_erifiability_scores}. Generally speaking, the packages with higher scores adopted more techniques to improve \textit{correctness}, and had better documents for us to verify it.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/correctness_verifiability_scores.png}
\caption{AHP correctness \& verifiability scores}
\label{fg_correctness_erifiability_scores}
\end{figure}

After examining the source code, we could not find any evidence of unit testing in more than half of the projects. Unit testing benefits most parts of the software's life cycle, such as designing, coding, debugging, and optimization \cite{Hamill2004}. It can reveal the bugs at an earlier stage of the development process, and the absence of unit testing may cause worse \textit{correctness \& verifiability}.

We could not find requirements specifications for most projects. The only document we found is a road map of \textit{3D Slicer}, which contained design requirements for the following changes. However, it did not record the conditions for previous versions. We also could not identify the theory manuals for all of the projects. It seems that even for some projects with well-organized documents, requirements specifications and theory manuals were still missing.

We identified five projects using continuous integration and continuous delivery (CI/CD) tools, which are \textit{3D Slicer}, \textit{ImageJ
}, \textit{Fiji}, \textit{dwv}, and \textit{OHIF Viewer}.

\section{Surface Reliability}
As described in Section \ref{sec_result_installability}, we could not build \textit{dwv} and \textit{GATE}. However, since there was an online or VM version of them, successful deployment is possible. So the failure of installation did not affect their scores in \textit{surface reliability}. Figure \ref{fg_reliability_scores} shows the AHP results.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/reliability_scores.png}
\caption{AHP surface reliability scores}
\label{fg_reliability_scores}
\end{figure}

When applying basic operations with the software packages, we found out that \textit{Drishti} crashed during loading damaged image files, and \textit{GATE} could not open macro files and lost response several times.

\section{Surface Robustness}
Figure \ref{fg_robustness_scores} presents the scores for \textit{surface robustness}.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/robustness_scores.png}
\caption{AHP surface robustness scores}
\label{fg_robustness_scores}
\end{figure}

The packages with higher scores elegantly handled the unexpected/unanticipated inputs, normally showing a clear error message. We might underestimate the score of \textit{OHIF Viewer} since we needed further customization to load data, and the test was not complete. \textit{MatrixUser}, \textit{dwv}, \textit{Slice:Drop}, and \textit{MRIcroGL} ignored the incorrect format of the input files, and displayed blank or meaningless images. \textit{Drishti} successfully detected the unexpected/unanticipated inputs, but the software crashed as a result. For unknown reasons, \textit{GATE} failed to load both correct and incorrect inputs.

\section{Surface Usability}
Figure \ref{fg_usability_scores} lists the AHP scores for \textit{surface usability}.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/usability_scores.png}
\caption{AHP surface usability scores}
\label{fg_usability_scores}
\end{figure}

We found a getting started tutorial for only 11 projects but a user manual for 22 projects. \textit{MRIcroGL} was the only one with expected user characteristics documented.

The ones with higher scores usually provided both comprehensive document guidance and a good user experience. \textit{INVESALIUS 3} set an excellent example of a detailed and precise user manual. \textit{GATE} also provided a large number of documents, but we think that they conveyed the ideas poorly, as we had trouble understanding and using them.

Table \ref{tab_user_support_model} shows the user support models by the number of projects using them. Maybe not every team intended to use GitHub issues to answer users' questions, but many users use them to seek help.

\begin{table}[H]
\centering
\begin{tabular}{ll}
\hline
\multicolumn{1}{c}{User support model} & Number of projects \\ \hline
GitHub issue & 24 \\
GitLab issue, SourceForge discussions & 2 \\
FAQ & 12 \\
Forum & 10 \\
E-mail address & 9 \\
Troubleshooting & 2 \\
Contact form & 1 \\ \hline
\end{tabular}
\caption{\label{tab_user_support_model}User support models by number of projects}
\end{table}

\section{Maintainability}
Figure \ref{fg_maintainability_scores} shows the AHP results for \textit{maintainability}.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/maintainability_scores.png}
\caption{AHP maintainability scores}
\label{fg_maintainability_scores}
\end{figure}

We marked \textit{3D Slicer} with a much higher score than others because it did very well at closing the identified issues, and more importantly, we found it to have the most comprehensive artifacts. For example, as far as we could find out, only a few of the 29 projects had a project plan, developer's manual, or API documentation, and only \textit{3D Slicer}, \textit{ImageJ}, \textit{Fiji} included all three documents. Meanwhile, \textit{3D Slicer} has a much higher percentage of closed issues (91.65\%) than \textit{ImageJ} (52.49\%) and \textit{Fiji} (63.79\%). Table \ref{tab_maintainability_docs} shows which projects had these documents.

\begin{table}[H]
\centering
\begin{tabular}{llll}
\hline
\multicolumn{1}{c}{Software} & Proj plan & Dev manual & API doc \\ \hline
3D Slicer & X & X & X \\
Weasis &  & X &  \\
SMILI &  &  & X \\
ImageJ & X & X & X \\
Fiji & X & X & X \\
dwv &  &  & X \\
BioImage Suite Web &  & X &  \\
OHIF Viewer &  & X & X \\
ParaView & X &  &  \\
INVESALIUS 3 & X &  &  \\
medInria &  & X &  \\
Gwyddion &  & X & X \\ \hline
\end{tabular}
\caption{\label{tab_maintainability_docs}Software with the maintainability documents}
\end{table}

27 of the 29 projects used git as the version control tool; \textit{AMIDE} used Mercurial; \textit{Gwyddion} used Subversion. 24 projects used GitHub for their repositories; \textit{XMedCon
}, \textit{AMIDE}, and \textit{Gwyddion} used SourceForge; \textit{DicomBrowser} and \textit{3DimViewer} used BitBucket.

\section{Reusability}
Figure 4.7 shows the AHP results for \textit{reusability}.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/reusability_scores.png}
\caption{AHP reusability scores}
\label{fg_reusability_scores}
\end{figure}

As described in Section \ref{sec_grading_template}, we gave higher scores to the projects with an API document and more code files. As shown in Table \ref{tab_maintainability_docs}, seven projects had API documents. Figure \ref{fg_num_text_files} shows the number of text-based files by projects.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/num_text_files.png}
\caption{Number of text-based files files by projects}
\label{fg_num_text_files}
\end{figure}

\section{Surface Understandability}
Figure \ref{fg_surface_understandability_scores} shows the scores for \textit{surface understandability}.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/understandability_scores.png}
\caption{AHP surface understandability scores}
\label{fg_surface_understandability_scores}
\end{figure}

All projects had a consistent code style with parameters in the same order for all functions; the code was modularized; the comments were clear, indicating what is being done, not how. However, we only found explicit identification of a coding standard for only 3 out of the 29, which are \textit{3D Slicer}, \textit{Weasis}, and \textit{ImageJ}. We also found hard-coded constants in \textit{medInria}, \textit{dicompyler}, \textit{MicroView}, and \textit{Papaya}. We did not find any reference to the used algorithms in projects \textit{XMedCon}, \textit{DicomBrowser}, \textit{3DimViewer}, \textit{BioImage Suite Web}, \textit{Slice:Drop}, \textit{MatrixUser}, \textit{DICOM Viewer}, \textit{dicompyler}, and \textit{Papaya}.

\section{Visibility/Transparency}
Figure \ref{fg_visibility_transparency_scores} shows the AHP scores for \textit{visibility/transparency}. Generally speaking, the teams that actively documented their development process and plans scored higher because they delivered better communication to people outside the team.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/visibility_transparency_scores.png}
\caption{AHP visibility/transparency scores}
\label{fg_visibility_transparency_scores}
\end{figure}

Table \ref{tab_Visibility/Transparency_docs} shows the projects which had documents for the development process, project status, development environment, and release notes.

\begin{table}[]
\centering
\begin{tabular}{lllll}
\hline
Software & Dev process & Proj status & Dev env & Rls notes \\ \hline
3D Slicer & X & X & X & X \\
Weasis \cite{Roduit2021} &  &  & X & X \\
MRIcroGL \cite{Rorden2021} &  &  &  & X \\
SMILI \cite{Chandra2018} &  &  &  & X \\
ImageJ \cite{Rueden2017} & X & X & X & X \\
Fiji \cite{Schindelin2012} & X & X & X &  \\
Horos \cite{horosproject2020} &  &  &  & X \\
OsiriX Lite \cite{PixmeoSARL2019} &  &  &  & X \\
dwv \cite{Martelli2021} &  &  &  & X \\
Drishti \cite{Limaye2012} &  &  &  & X \\
\begin{tabular}[c]{@{}l@{}}BioImage Suite\\ Web\end{tabular} &  &  & X &  \\
OHIF Viewer \cite{Ziegler2020} &  &  & X & X \\
GATE \cite{Jan2004} &  &  &  & X \\
ITK-SNAP \cite{Yushkevich2006} &  &  &  & X \\
ParaView \cite{Ahrens2005} &  & X &  &  \\
MatrixUser \cite{Liu2016} &  &  &  & X \\
DICOM Viewer \cite{Afsar2021} &  &  & X & X \\
INVESALIUS 3 \cite{Amorim2015} &  &  &  & X \\
medInria \cite{Fillard2012} &  &  & X & X \\
MicroView \cite{ParallaxInnovations2020} &  &  &  & X \\
Gwyddion \cite{Nevcas2012} &  &  &  & X \\ \hline
\end{tabular}
\caption{\label{tab_Visibility/Transparency_docs}Software with the visibility/transparency documents}
\end{table}

\section{Overall Scores}

As described in Section \ref{sec_AHP}, for our AHP measurements, there are nine criteria which are the nine software qualities and 29 software packages as the alternatives. We decided to make all nine qualities equally important, so the score of each quality affects the overall scores on the same scale.

Figure \ref{fg_overall_scores} shows the overall scores of all 29 software packages in descending order. Since we produced the scores from the AHP process, the total sum of the 29 scores is precisely 1.

\begin{figure}[H]
\includegraphics[scale=0.38]{figures/overall_scores.png}
\caption{Overall AHP scores for all 9 software qualities}

\label{fg_overall_scores}
\end{figure}

The top software products had higher scores in most criteria. For example, \textit{3D Slicer} ranked in the top two software products for all qualities except \textit{surface robustness}; \textit{ImageJ} ranked in the top three products for \textit{correctness \& verifiability}, \textit{surface reliability}, \textit{surface usability}, \textit{maintainability}, \textit{ surface understandability}, and \textit{visibility/transparency}; \textit{OHIF Viewer} ranked in the top five products for \textit{correctness \& verifiability}, \textit{surface reliability}, \textit{surface usability}, \textit{maintainability}, and \textit{reusability}. We might underestimate its scores of two qualities for \textit{DICOM Viewer}, but equally compared it with the other software for the rest seven qualities.

### 2021-07-24 StateOfPractice/Ao-Report/15InterviewsWithDevelopers.tex
minor update
MI report - updated ch 4

In this section, we only discuss the answers which we think are the most exciting and essential. We summarize the rest part of the interviews in Appendix \ref{ap_interview}. The interviewees may have provided multiple answers to each question. When counting the number of interviewees for each response, we count all of them with this answer.

@@

\textit{Proven solutions from interviewees:}
\begin{itemize}
\item GitHub Actions, which is a good continuous integration and continuous delivery (CI/CD) tool to save time.
\end{itemize}

>>>>

In this section, we only discuss the answers which we think are the most exciting and essential. We summarize the rest part of the interviews in Appendix \ref{ap_interview}. The interviewees may have provided multiple answers to each question. When counting the number of interviewees for each response, we count every interviewee with this answer.

@@

\textit{Proven solutions from interviewees:}
\begin{itemize}
\item GitHub Actions, which is a good CI/CD tool to save time.
\end{itemize}
